Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Implementation: Testing examples: wording

To verify examples, Doctest uses GHCi.
Test is done by comparing result string in Haddock notation and
result string from GHCi.
Since verification based on string comparison, exceptions can be handled.

Doctest reuses the same GHCi session for all examples.
Examples from the same Haddock comment are grouped together,
and share the same scope.
The scope is cleared with \verb|:reload| before a new
example group is started.

>>>>

Doctest uses GHCi to verify examples.  Verification is done by
comparing the expected output given in the Haddock comment with the
actual output of GHCi.  Since verification is based on string
comparison, exceptions can be handled.

Doctest reuses the same GHCi session for all examples.
Examples from the same Haddock comment are grouped together,
and share the same scope.
Doctest clears the scope with \verb|:reload| before it tests a new
example group.
